Local Spectral Clustering of Density Upper Level Sets

### 2019-05-10 arxiv/arxiv_local_density_clustering.tex
updated mixing time proof and section, edited other sections

%%% Probability distributions (and related items)
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Cbb}{\mathbb{C}}

@@

\item Under \textcolor{red}{largely the same set of geometric conditions}, we derive in Theorem
  \ref{thm: inverse_mixing_time_lower_bound_nonconvex} a lower bound on the
  inverse mixing time of a random walk over $\Csig[\Xbf]$.

@@

\item
\label{asmp: cluster_diameter}
\emph{Cluster diameter:}
There exists $D < \infty$ such that for all $x, x' \in \Csig$,
$$
\norm{x - x'} \leq D.
$$

\item
\label{asmp: biLipschitz_mapping}
\emph{biLipschitz mapping to convex set:}
There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
\begin{equation*}
\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
\end{equation*}
such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
\end{enumerate}

Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
clusters and long clusters in \ref{asmp: bounded_density} and \ref{asmp:
  cluster_diameter}, flat densities around the level set in \ref{asmp: 
  low_noise_density}, and poorly separated clusters in \ref{asmp:
  cluster_separation}.

Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
\ref{asmp: cluster_separation} and \ref{asmp: biLipschitz_mapping} are used to upper bound $\Phi(\Cset[\Xbf];
G_{n,r})$, whereas \ref{asmp: bounded_density}, \ref{asmp: cluster_diameter} and \ref{asmp: biLipschitz_mapping} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
cluster_separation} are similar to the $(\sigma,\epsilon)$-saliency of
\citep{chaudhuri2010}, a standard density clustering assumption, while
\ref{asmp: low_noise_density} is seen in, e.g., \citep{singh2009} (as well as
many other works on density clustering and level set estimation.)  It is worth
highlighting that these assumptions are all local in nature, a benefit of
studying a local algorithm such as \ppr.

@@

\begin{theorem}
\label{thm: conductance_upper_bound}
Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
and \ref{asmp: cluster_separation}, for some 
$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/4d$ be such that
\begin{equation}
\label{eqn: weighted_cluster_volume}
\pi_{\Pbb,r}(\Csig) \leq \frac{1}{2}.
\end{equation}
 Then for any $0 < \delta < 1$, $\epsilon > 0$, if
\begin{equation}
\label{eqn: conductance_sample_complexity}
n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
  {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
\end{equation}
then
\begin{equation}
  \label{eqn: conductance_additive_error_bound}
  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c \frac{d}{\sigma}
  \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
    c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
\end{equation}
with probability at least $1-\delta$.
\end{theorem}

\begin{remark}
The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other
proofs in this paper, can be found in the supplementary document. The key 
idea is that for any $x \in \Cset$, the simple (possibly loose) fact
$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Csig + rB) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
  low_noise_density} to find a corresponding bound on the weighted volume,
then apply standard concentration inequalities to convert from population-
to sample-based results.  
\end{remark}

\begin{remark}
The inequality in \eqref{eqn: conductance_additive_error_bound} is almost
tight. Specifically, choosing $\Asig = B(0,\sigma)$ and
$$
 f(x)  = \begin{cases}
   \lambda &\text{for $x \in \Asig$}, \\
   \lambda - \dist(x,\Asig)^{\gamma} & \text{ for $0 < \dist(x,\Asig) < r$}, 
\end{cases}
$$
we have that for $n$ on the order of the lower bound in \eqref{eqn: 
  conductance_sample_complexity}, 
$$
  \frac{\Phi_{n,r}(\Asig[\mathbf{X}])}{r} \geq c \frac{(\lambda -
    \frac{r^{\gamma+1}}{\gamma+1})}{\lambda} - \epsilon,
$$
with probability at least $1 - \delta$, for some constant $c$. (Note that the
factor of $1 / \sigma$ in $c_{\sigma}$ is not replicated above.)
\end{remark}

@@

Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of 
$\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) =
1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time. 
% RJT: note I changed the next two theorems to be upper bounds on the mixing
% time.  Upper bounds on the inverse inverse mixing time, which was a bit
% superfluous.  Just make sure that the supplement is in sync with this
% AJG: Perfect.

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound_nonconvex}
Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
Assumptions \ref{asmp: bounded_density} and \ref{asmp: cluster_diameter} 
for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D > 0$. Then for any $0 <
r < \sigma/(4d)$, $0 < \delta < 1$, $\epsilon > 0$, and $n$ satisfying 
$$
\sqrt{3^{d+1}\frac{(\log n + d\log \mu + \log(4/\delta))}{n \nu_d r^d
    \lambda_{\sigma}}} \leq \epsilon, 
$$
where \smash{$\mu = \log(\frac{2D}{r})$}, we have
\begin{multline}
\label{eqn: inverse_mixing_time_lower_bound_nonconvex}
\tau_{n,r}(\Csig[\Xbf]) \leq (d \log \mu + c_{\lambda}) \cdot \\  
\left(c_1 + 9^d c_2 \frac{\Lambda_{\sigma}^4D^{2d}}{\lambda_{\sigma}^4r^{2d}}\left(d
    \log \mu + c_{\lambda}\right)\right),
\end{multline}
with probability at least $1 - \delta$, where $c_1,c_2>0$ are universal constants
 and $c_{\lambda} = \log(\Lambda_{\sigma}^2/ 
\lambda_{\sigma}^2)$.   
\end{theorem}
% RJT: saying that c_1,c_2 depend on the dimension is a little odd/weak.
% c_2 multiplyies, e.g., a factor of d \log \mu.  So if it's d^{10}, then this
% will swamp the linear factor of ....
% AJG: Fixed.

\begin{remark}
The proof of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} relies
on upper bounding the mixing time using the \emph{conductance} of $G_{n,r}[\Csig[\Xbf]]$, 
$$
\widetilde{\Phi} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; G_{n,r}[\Csig[\Xbf]]).
$$
The factor of $1/r^{2d}$ in the bound in \eqref{eqn:
  inverse_mixing_time_lower_bound_nonconvex} is suboptimal. This exponential 
dependence on $d$ stems from a loose bound on the aforementioned
conductance. In particular, we assert only that any set $S \subseteq \Csig[X]$
must have $\cut(S; \Csig[\Xbf])$ on the order of $n^2 r^{2d}$, while upper bounding
$\vol(S; \Csig[\Xbf])$ by roughly $n^2 r^d$, for a bound on the conductance of
order $r^d$. The presence of $r^{2d}$ comes from upper bounding the mixing time
by about \smash{$1/\widetilde{\Phi}^2$}, this being a variant of classic results
on rapid mixing \citep{jerrum89}.  
\end{remark}

\subsection{Tighter Lower Bound Under Convexity}

It is possible to sharpen the dependency on $d$ in 
\eqref{eqn: inverse_mixing_time_lower_bound_nonconvex}, but at the cost of an  
additional assumption.
\begin{enumerate}[label=(A\arabic*)]
\setcounter{enumi}{4}
\item 
\label{asmp: convex}
\emph{Convexity:} The set $\Cset_\sigma$ is convex. 
\end{enumerate}

With \ref{asmp: convex} in place, we give a tighter bound on the
mixing time (albeit one that holds only asymptotically).

\begin{theorem}
\label{thm: inverse_mixing_time_lower_bound}
Assume the conditions of Theorem \ref{thm:
  inverse_mixing_time_lower_bound_nonconvex}, and additionally, \ref{asmp:
  convex}. Then for any $0 < r < \sigma/4d$, the following holds with
probability 1:   
\begin{align}
\label{eqn: inverse_mixing_time_lower_bound}
  \limsup_{n \to \infty} \, &\tau_{n,r}(\Csig[\Xbf]) \leq \nonumber \\ 
&\quad c_1 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\log \mu +
  c_{\lambda}) \biggl( c_{\lambda}(d^3 \log\mu + c_2) +{} \nonumber \\  
&\quad \frac{d^2D^2}{r^2} \bigl( \log d + c_2
  \frac{\Lambda_{\sigma}^{2}}{\lambda_{\sigma}^{2}}c_{\lambda} +{} \nonumber \\  
&\quad c_3  + \log \log \mu \bigr) \biggr) + c_d \frac{o_r(1)}{r^2},
\end{align}
where \smash{$\mu = \log(\frac{2D}{r})$}, $c_1,c_2,c_3>0$ are universal
constants, $c_d$ is constant in $r$ but depends on dimension $d$, and
$c_{\lambda} = \log(\Lambda_{\sigma}^2/ \lambda_{\sigma}^2)$.  
% Additionally, $\lim_{r \to 0} o_r(1) = 0$.  
\end{theorem}

\begin{remark}
The only potentially exponential dependence on dimension comes from the
factor of $c_d$. However, for sufficiently small values of $r$ $o_r(1)/r^2$ will be dominated by $1/r^2$, and therefore the last term in \eqref{eqn: inverse_mixing_time_lower_bound} will contribute negligibly to the overall bound.
\end{remark}
\begin{remark}
We achieve superior rates in Theorem \ref{thm: inverse_mixing_time_lower_bound}
to those of Theorem \ref{thm: inverse_mixing_time_lower_bound_nonconvex} in part 
by working with a generalization of the conductance, the \emph{conductance
  function},
$$
\widetilde{\Phi}_{n,r}(t) = 
\min_{\substack{S \subseteq \Csig[\Xbf] \\ \widetilde\pi(S) \leq t}} 
\Phi(S; G_{n,r}[\Csig[X]]),
$$
where \smash{$\widetilde\pi$} is the stationary distribution over
$G_{n,r}[\Csig[\Xbf]]$. The utility of the conductance function comes from the
known upper bound of mixing time by  
\begin{equation}
\label{eqn: average_conductance}
\int \frac{1}{t \widetilde{\Phi}_n(t)^2} dt,
\end{equation}
which results in a tighter bound than merely using the conductance when
\smash{$\widetilde{\Phi}_n(t)$} is large for small values of $t$.

Our proof relies on a novel (to the best of our knowledge) lower bound
on this conductance function over $G_{n,r}$ in terms of a population-level
analogue, which we denote \smash{$\widetilde{\Phi}_{\Pbb,r}$}, and define formally in the supplementary document.
\begin{lemma}
	\label{lem: consistency_of_conductance_function_main}
	Fix $0 < t < 1/2$. Under the conditions on $\Csig$ given by Theorem \ref{thm: inverse_mixing_time_lower_bound}, the following statement holds: with probability one, as $n \to \infty$,
	\begin{equation}
	\label{eqn: pointwise_consistency_of_conductance_function}
	\liminf_{n \to \infty} \widetilde{\Phi}_{n,r}(t) \geq \min\left\{\widetilde{\Phi}_{\Pbb,r}(t), c_d r \omega_r(1)\right\}
	\end{equation}
	where $c_d$ is the same as in Theorem \ref{thm: inverse_mixing_time_lower_bound}.
\end{lemma}
Plugging
\smash{$\widetilde{\Phi}_{\Pbb,r}$} into \eqref{eqn: average_conductance} yields
a mixing time bound (with respect to total variation distance) on the order $d 
D^2/r^2 + d^2\log(D/r)$ over convex sets. By contrast, \eqref{eqn:
  inverse_mixing_time_lower_bound} is of order $d^2 D^2/r^2 + d^3\log(D/r)$ 
(ignoring the $o_r(1)$ term) but handles mixing time with respect to relative
pointwise distance (which is known to be a stricter metric). 
\end{remark}

\begin{remark}
  The convexity condition is only needed to lower bound 
  \smash{$\widetilde{\Phi}_{\Pbb,r}$}. Any lower bound on
  \smash{$\widetilde{\Phi}_{\Pbb,r}$} could be directly plugged into the 
  machinery of the proof of Theorem \ref{thm: inverse_mixing_time_lower_bound}
  to yield an alternative result. In recent work, \citep{abbasi-yadkori2016} developed new
  population-level bounds on the conductance function (without requiring
  convexity), however the Markov chain dealt with there is somewhat different 
  than the one we consider.    
\end{remark}

@@

For \pprspace to accurately estimate a set, the ratio of normalized cut to inverse mixing time should be small. Letting $\theta := (\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the rates in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound}, further let
\begin{align*}
\mathbf{\Phi}(\theta) 
& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \\
\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^8}{\lambda_{\sigma}^8} (\mu + c_{\lambda}) \biggl( c_{\lambda}(d^3 \mu + c_3) + \frac{d^2D^2}{r^2} \Bigl( \log d + c_3 \frac{\Lambda_{\sigma}^2}{\lambda_{\sigma}^2} c_{\lambda} + c_4 + \log \mu \Bigr) \biggr) \Biggr)^{-1}
\end{align*}
(where all constants $c_0,c_1,c_2,c_3,c_4,c_\lambda>0$ are as in these 
theorems).

Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf(\theta)$ and $\Psibf(\theta)$.
\begin{definition}[Well-conditioned density clusters]
	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: biLipschitz_mapping} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}. Then, setting
	\begin{equation*}
	\kappa(\Cset) := \frac{\mathbf{\Phi}(\theta)}{\mathbf{\Psi}(\theta)}
	\end{equation*}
	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster (with respect to $\theta$).}
\end{definition}

$\Phibf(\theta)$ and $\Psibf(\theta)$ are familiar; they are exactly the upper and lower bounds on $\Phi_{n,r}(\Csig[\Xbf])$ and $\Psi_{n,r}(\Csig[\Xbf])$ derived in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: inverse_mixing_time_lower_bound_nonconvex}, respectively.

\textcolor{red}{Add a remark here, about how this reinforces the results of Gary Miller and others, that PPR can fail to pick up fat sets even when normalized cut properly identifies them.}

@@

In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
\begin{align}
\label{eqn: initialization}
\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta), & ~r \leq \frac{\sigma}{2d} \nonumber,  \\
\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, & ~v \in \Csig[\Xbf]^g
\end{align}
where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g) \geq \vol(\Csig[\Xbf])/2$. (Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)

@@

\textcolor{red}{Add a remark here, detailing how one might go about picking these parameters in practice.}

@@

To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on \textcolor{red}{misclassification rate}, we make further boundedness restrictions on the density $f$ to preclude vertices $x \in \Xbf$ with arbitrarily small degree. Namely,

\begin{equation}
\label{eqn: global_bounded_density}
0 < \lambda_{\min} \leq f(x)
\end{equation}

\begin{theorem}
	\label{thm: misclassification_rate}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$). Then, with probability tending to one as $n \to \infty$,
	\begin{equation}
	\label{eqn: misclassification_rate_ub}
	\frac{\abs{\Csig[\Xbf] \setminus \widehat{C}}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}
	\end{equation}
	and
	\begin{equation}
	\label{eqn: misclassification_rate__ub_2}
	\frac{\abs{\widehat{C} \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
	\end{equation}
	for universal constants $c_5, c_6 > 0$. 
\end{theorem}

>>>>

%%% Probability distributions (and related items)
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Cbb}{\mathbb{C}}
\newcommand{\Ebb}{\mathbb{E}}

@@

\item Under \textcolor{red}{largely the same set of geometric conditions}, we derive in Theorem
  \ref{thm: inverse_lower_bound_nonconvex} a lower bound on the
  inverse mixing time of a random walk over $\Csig[\Xbf]$.

@@

\item
\label{asmp: embedding}
\emph{Lipschitz embedding:}
There exists $\mathcal{K} \subseteq \Rd$ convex, and $g: \Reals^d \to \Reals^d$ satisfying
\begin{equation*}
\det(\nabla g (x) ) = 1,\frac{1}{L}\norm{x - y} \leq \norm{g(x) - g(y)} \leq L \norm{x - y} ~ \text{for all $x,y \in \Reals^d$}
\end{equation*}
such that $\Csig$ is the image of $\mathcal{K}$ by $g$, $\Csig = g(\mathcal{K})$.
Furthermore, there exists $D < \infty$ such that for all $x, x' \in \mathcal{K}$
$$
\norm{x - x'} \leq D.
$$
\end{enumerate}

Note that $\sigma$ plays several roles here, precluding arbitrarily narrow
clusters and long clusters in \ref{asmp: bounded_density}, flat densities around the level set in \ref{asmp: low_noise_density}, and poorly separated clusters in \ref{asmp: cluster_separation}.

Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
and \ref{asmp: cluster_separation} are used to upper bound $\Phi(\Cset[\Xbf];
G_{n,r})$, whereas \ref{asmp: bounded_density}, and \ref{asmp: embedding} are required to lower bound $\Psi(\Cset[\Xbf]; G_{n,r})$. We note that the
lower bound on minimum density in \ref{asmp: bounded_density} along with \ref{asmp:  
cluster_separation} are similar to the $(\sigma,\epsilon)$-saliency of
\citep{chaudhuri2010}, a standard density clustering assumption, while
\ref{asmp: low_noise_density} is seen in, e.g., \citep{singh2009} (as well as
many other works on density clustering and level set estimation.)  It is worth
highlighting that these assumptions are all local in nature, a benefit of
studying a local algorithm such as \ppr.

@@

\begin{theorem}
\label{thm: conductance_upper_bound}
Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy
Assumptions \ref{asmp: bounded_density}, \ref{asmp: low_noise_density},
and \ref{asmp: cluster_separation}, for some 
$\sigma, \lambda_{\sigma}, c_0, \gamma > 0$. Let $0 < r \leq \sigma/4d$ be such that
\begin{equation}
\label{eqn: weighted_cluster_volume}
\pi_{\Pbb,r}(\Csig) \leq \frac{1}{2}.
\end{equation}
 Then for any $0 < \delta < 1$, $\epsilon > 0$, if
\begin{equation}
\label{eqn: conductance_sample_complexity}
n \geq \frac{(2+\epsilon)^2\log(3/\delta)}{\epsilon^2}\left(\frac{25}
  {6 \lambda_{\sigma}^2\nu(\Csig) \nu_d r^d}\right)^2,
\end{equation}
then
\begin{equation}
  \label{eqn: conductance_additive_error_bound}
  \frac{\Phi_{n,r}(\Csig[\mathbf{X}])}{r} \leq c \frac{d}{\sigma}
  \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} -
    c_0\frac{r^{\gamma}}{\gamma+1})}{\lambda_{\sigma}} + \epsilon, 
\end{equation}
with probability at least $1-\delta$ (where $c_1 > 0$ is a universal constant).
\end{theorem}

\begin{remark}
The proof of Theorem \ref{thm: conductance_upper_bound}, along with all other
proofs in this paper, can be found in the supplementary document. The key 
idea is that for any $x \in \Cset$, the simple fact
$B(x,\sigma) \subseteq \Csig$ translates into the upper bound $\nu(\Csig + rB) \leq (1 + 2d r /\sigma)\nu(\Csig)$. We leverage \ref{asmp:
  low_noise_density} to find a corresponding bound on the weighted volume,
then apply standard concentration inequalities to convert from population-
to sample-based results.  
\end{remark}

\begin{remark}
The inequality in \eqref{eqn: conductance_additive_error_bound} is tight in the case of $\Cset = \set{0}$. To see this, let $\Csig = B(0,\sigma)$ and
$$
 f(x)  = \begin{cases}
   \lambda &\text{for $x \in \Csig$}, \\
   \lambda - \dist(x,\Csig)^{\gamma} & \text{ for $0 < \dist(x,\Csig) < r$}, 
\end{cases}
$$
Then, some simple calculations yield
\begin{equation*}
\frac{\Pbb((\Csig + B(0,r)) \setminus \Csig)}{\Pbb(\Csig)} \geq d\frac{(\lambda - r^{\gamma}) r}{\sigma},
\end{equation*}
and for some $c > 0$,
\begin{equation*}
\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) \setminus \Csig) \geq c \lambda \nu_d r^d \Pbb((\Csig + B(0,r)), \quad \textrm{and} \quad \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r}) \leq c \lambda \nu_d r^d \Pbb(\Csig)
\end{equation*}
so the ratio $\Ebb(\cut(\Csig[\Xbf]; G_{n,r})) / \Ebb(\vol_{n,r}(\Csig[\Xbf]; G_{n,r})$ matches \ref{eqn: conductance_additive_error_bound}, up to constants.

\end{remark}

@@

Next we lower bound the inverse mixing time \eqref{eqn: inv_mixing_time} of $\Csig[\Xbf]$, or equivalently, as $\Psi_{n,r}(\Csig[\Xbf]) = 1/\tau_{n,r}(\Csig[\Xbf])$, we upper bound the mixing time.

\begin{theorem}
	\label{thm: mixing_time_upper_bound}
	Fix $\lambda > 0$, and let $\Cset \in \Cbb_f(\lambda)$ satisfy Assumptions \ref{asmp: bounded_density} and \ref{asmp: embedding} for some $\sigma, \lambda_{\sigma}, \Lambda_{\sigma}, D, K > 0$. Then, for any $0 < r < \sigma/2\sqrt{d}$, with probability one
	\begin{equation*}
	\limsup_{n \to \infty}\tau_{n,r}(\Csig[\Xbf]) \leq c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right)
	\end{equation*}
\end{theorem}
for $c_2,c_3 > 0$ universal constants.

We will outline the main techniques used to prove Theorem \ref{thm: mixing_time_upper_bound}, but first, we show that a straightforward and perhaps immediately obvious route to upper bounding the mixing time is insufficient for our purposes. Let $\widetilde{\Phi}_{n,r}$ be the \emph{conductance} of the induced subgraph $\widetilde{G}_{n,r} = G_{n,r}\bigl[\Csig[\Xbf]\bigr]$, given by
\begin{equation*}
\widetilde{\Phi}_{n,r} = \min_{S \subseteq \Csig[\Xbf]} \Phi(S; \widetilde{G}_{n,r}),
\end{equation*}
and $\widetilde{\mu}_2$ be the 2nd largest eigenvalue of $\Wbf_{\Csig[\Xbf]}$, the random walk matrix over $\widetilde{G}_{n,r}$. The famous Cheeger's inequality
\begin{equation*}
\frac{\widetilde{\Phi}_{n,r}^2}{2} \leq 1 - \widetilde{\mu}_2 \leq \widetilde{\Phi}_{n,r}
\end{equation*}
applied with well known theory on $\infty$-mixing time yields
\begin{equation*}
\abs{\widetilde{\pi}_{n,r}(u) - e_v \Wbf_{\Csig[\Xbf]}^te_u} \leq \left(1 - \frac{\widetilde{\Phi}_{n,r}^2}{2}\right)^t \sqrt{\frac{\deg(u; \widetilde{G}_{n,r})}{\min_{v \in \Csig[\Xbf]} \deg(v; \widetilde{G}_{n,r})}} \tag{$u,v \in \Csig[\Xbf]$}
\end{equation*}
where $\widetilde{\pi}_{n,r}$ is the stationary distribution over $\widetilde{G}_{n,r}$ Unfortunately, even if $\widetilde{G}_{n,r}$ is an approximately degree-regular graph, (meaning we can ignore the term under the square root), this bound only yields \footnote{For sequences of numbers $\set{a_n}_{n \in \mathbb{N}}, \set{b_n}_{n \in \mathbb{N}}$, we say $a_n = \mathcal{O}(b_n)$ when there exists $c$ sufficiently large such that $a_n \leq c b_n$ for all $n$.}
\begin{equation*}
\tau_{n,r}(\Csig[\Xbf]) = \mathcal{O} \left( \frac{\log\left(\frac{1}{\widetilde{\pi}_{\min}}\right)}{\widetilde{\Phi}_{n,r}^2} \right).
\end{equation*}
where $\widetilde{\pi}_{\min} = \min_{u \in \Csig[\Xbf]} \widetilde{\pi}_{n,r}(u)$. As $\widetilde{\pi}_{\min} = \mathcal{O}(1/n)$, the upper bound on the right hand side will be of order $\log(n)$, and the bound becomes trivial as $n \to \infty$.

\textcolor{red}{We therefore apply a more complex approach.}

@@

For \pprspace to accurately estimate a set, the ratio of normalized cut to inverse mixing time should be small. Letting $\theta := (r, \sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L)$ contain those parameters which govern the bounds given in Theorems \ref{thm: conductance_upper_bound} and \ref{thm: mixing_time_upper_bound}, further abbreviate
\begin{align*}
\mathbf{\Phi}(\theta) 
& := c_1 r \frac{d}{\sigma} \frac{\lambda}{\lambda_{\sigma}} \frac{(\lambda_{\sigma} - c_0 \frac{r^{\gamma}}{\gamma + 1})}{\lambda_{\sigma}} \\
\mathbf{\Psi}(\theta) & := \Biggl(c_2 \frac{\Lambda_{\sigma}^4 d^3 D^2 L^2}{\lambda_{\sigma}^4 r^2} \log^2\left(\frac{1}{r}\right) + c_3 \log\left(\frac{\Lambda_{\sigma}}{\lambda_{\sigma}}\right) \Biggr)^{-1}
\end{align*}
for these bounds (where all constants $c_0,c_1,c_2,c_3 >0$ are as in these theorems).

Well-conditioned density clusters satisfy all of the given assumptions, for parameters which results in `good' values of $\Phibf(\theta)$ and $\Psibf(\theta)$.
\begin{definition}[Well-conditioned density clusters]
	For $\lambda > 0$ and $\Cset \in \Cbb_f(\lambda)$, let $\Cset$ satisfy \ref{asmp: bounded_density} - \ref{asmp: embedding} for some $\sigma, \lambda, \lambda_{\sigma}, \Lambda_{\sigma}, \gamma, D, L > 0$, and additionally let $\Csig$ satisfy \eqref{eqn: weighted_cluster_volume}. Then, setting
	\begin{equation*}
	\kappa(\Cset) := \frac{\mathbf{\Phi}(\theta)}{\mathbf{\Psi}(\theta)}
	\end{equation*}
	we call $\Cset$ a \textrm{$\kappa$-well-conditioned density cluster (with respect to $\theta$).}
\end{definition}

We focusing for a moment on the neighborhood graph radius $r$. While taking $r \to 0$ as $n \to \infty$ -- and thereby ensuring $G_{n,r}$ is sparse-- is computationally attractive, the presence of a factor of $\frac{1}{r}$ in $\kappa(\Cset)$ unfortunately prevents us from making claims about the behavior of \pprspace for this regime. While the restriction to a kernel function fixed in $n$ is standard for theoretical analysis \cite{schiebinger2015,vonluxburg2008}, it is an interesting question whether \pprspace exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if this is merely looseness in our upper bounds.

\paragraph{Well-conditioned clusters.}

@@

In particular, for a well conditioned density cluster $\Cset$ (with respect to some $\sigma, \lambda_{\sigma}, \gamma, \Lambda_{\sigma}$ and $D$), we require
\begin{align}
\label{eqn: initialization}
\alpha \in [1/10, 1/9] \cdot \mathbf{\Psi}(\theta), & ~r \leq \frac{\sigma}{2d} \nonumber,  \\
\vol_0 \in [3/4,5/4] \cdot n(n-1) \int_{\Csig} \Pbb(B(x,r)) f(x) dx, & ~v \in \Csig[\Xbf]^g
\end{align}
where $\Csig[\Xbf]^g \subseteq \Csig[\Xbf]$ is some 'good' subset of $\Csig[\Xbf]$ which, as we will see, satisfies $\vol(\Csig[\Xbf]^g; G_{n,r}) \geq \vol(\Csig[\Xbf]; G_{n,r})/2$. (Intuitively one can think of $\Csig[\Xbf]^g$ as consisting of the nodes sufficiently close to the center of $\Csig[\Xbf]$, although we provide no formal justification to this effect.)

@@

%%% AJG 5/8/19: My attempt to explain how to choose these parameters
%%% in practice. Not satisfied with it.

In practice, a reasonable way to choose these hyperparameters is by tuning. For example, if one wanted to successfully recover a density cluster, one could vary each hyperparameter over a grid, retaining outputs $\widehat{\Cset}$ of Algorithm \ref{alg: ppr} only if they recover $\Cset[\Xbf]$ for some $\Cset \in \Cbb_f(\lambda)$ and discarding them otherwise. Then simply return the minimum normalized cut set from those $\widehat{\Cset}$ which were retained. Assuming there existed $\lambda > 0, \Cset \in \Cbb_f(\lambda)$ such that $\Cset$ satisfied the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, and moreover some combination of tuning parameters in the chosen grid satisfied \eqref{eqn: initialization}, this scheme would inherit the consistency guarantees of Theorem \ref{thm: consistent_recovery_of_density_clusters}.

@@

To translate \eqref{eqn: graph_symmetric_set_difference} into meaningful bounds on misclassification rate, we wish to preclude vertices $x \in \Xbf$ from having arbitrarily small degree. To do so, we make some regularity assumptions on $\mathcal{X} = \mathrm{supp}(f)$.
\begin{enumerate}[label=(A\arabic*)]
	\setcounter{enumi}{4}
	\item 
	\label{asmp: valid_region}
	\emph{Valid region:} $0 < \lambda_{\min} < f(x)$ for all $x \in \mathcal{X}$. Additionally, there exists some $c > 0$ such that for each $x \in \partial \mathcal{X}$, $\nu(B(x,r) \cap \mathcal{X}) \geq c\nu(B(x,r))$.
\end{enumerate}
Note that the latter condition in $\ref{asmp: valid_region}$ will be satisfied if, for instance, $\mathcal{X}$ is a $\sigma$-expansion.

\begin{theorem}
	\label{thm: misclassification_rate}
	Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a $\kappa$-well conditioned density cluster (with respect to some $\theta$), and additionally assume $f$ satisfies \ref{asmp: valid_region}. Then, with probability tending to one as $n \to \infty$,
	\begin{equation}
	\label{eqn: misclassification_rate_ub}
	\frac{\abs{\Csig[\Xbf] \setminus \widehat{C}}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_5 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\sigma}}
	\end{equation}
	and
	\begin{equation}
	\label{eqn: misclassification_rate_ub_2}
	\frac{\abs{\widehat{C} \setminus \Csig[\Xbf]}}{\Bigl|\Csig[\Xbf]\Bigr|} \leq c_6 \kappa(\Cset) \frac{\Lambda_{\sigma}}{\lambda_{\min}}.
	\end{equation}
	for universal constants $c_5, c_6 > 0$. 
\end{theorem}
